---
title: "DATA ANALYSES (TRANSMISSION CHAIN EXPERIMENT ON THE TRANSMISSION OF DOMINANCE, PRESTIGE AND MIDDLE SOCIAL RANK CUES"
author: "Angel V. Jimenez"
date: "04 December 2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analyses following preregistered data script on https://osf.io/68vcs 

## DATA
```{r}
# Read raw dataset
d<-read.csv("process_raw_data.csv")
```


```{r}
# DEMOGRAPHICS (ALL PARTICIPANTS)
# Frequencies by gender
summary(d$Gender)
# Range of ages
range(d$Age) 
# Mean of age
mean(d$Age) 
# Standard Deviation of age
sd(d$Age) 
# Histogram for age
# Histogram for age
breaks<-c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65)
hist(d$Age,
     main="Histogram for Age",
     xlab="Age",
     breaks = breaks,
     xlim=c(10,65),
     ylim=c(0,30),
     prob = FALSE,
     xaxt ="n")
axis(side=1, at=seq(15,65, 5), labels=seq(15,65,5))


```
```{r}
# DEMOGRAPHICS (INCLUDED PARTICIPANTS)
library(tidyverse)
d<-filter(d,DELETED == "NO")
# Frequencies by gender
summary(d$Gender)
# Range of ages
range(d$Age) 
# Mean of age
mean(d$Age) 
# Standard Deviation of age
sd(d$Age) 
# Histogram for age
# Histogram for age
breaks<-c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65)
hist(d$Age,
     main="Histogram for Age",
     xlab="Age",
     breaks = breaks,
     xlim=c(10,65),
     ylim=c(0,30),
     prob = FALSE,
     xaxt ="n")
axis(side=1, at=seq(15,65, 5), labels=seq(15,65,5))


```
# INTEREST IN FOOTBALL BY GENDER (#EXPLORATORY-NOT INCLUDED IN PREREGISTRATION)

```{r}
library(tidyverse)
d%>%
  group_by(Gender) %>%
  summarise(mean=mean(Football_1), sd=sd(Football_1), median=median(Football_1), min=min(Football_1), max=max(Football_1))

library(lattice)
histogram(~ Football_1 | Gender,  main= "Interest in Football", xlab="Score in the Scale", ylab="Frequency", col="grey", border="black",data=d)

library(ggplot2)
ggplot(d, aes(x=Gender, y=Football_1)) + 
  geom_boxplot(size=1) + 
  labs (x = "Gender", y ="Interest in Football")+
  theme_classic(base_size = 14)+expand_limits(y=c(0,7))


```



# NEW RECALL CODING SYSTEM (DIFFERENT FROM THE PROPOSED IN PREREGISTRATION)

```{r}
d<-read.csv("process_raw_data_included.csv")
```



```{r}
# Relabel Individual categories

d$CUE<-d$INDIVIDUAL
d$CUE<- ifelse((d$CUE=="JOHN"),"Prestige",
                              ifelse((d$CUE=="BILL"),"Dominance", "Middle Rank"))
```





```{r}
# Creation of colorblind-friendly pallette
cbPalette <- c("#D55E00", "#E69F00", "#56B4E9", "#009E73", "#999999", "#CC79A7")
# Chain plots
library(ggplot2)
(chain_plot<-ggplot(d, aes(GENERATION_FACTOR, RECALL, colour = CUE)) + stat_summary(fun.y = mean, geom = "line", size = 1.3, aes(group = CUE, colour = CUE)) + stat_summary(fun.y = mean, geom = "point", size = 1, aes(shape = CUE)) + theme_classic() + facet_wrap(~ CHAIN) + theme_classic(base_size = 10) + labs(x = "Experimental Transmission Chain Generation", y = "Number of Correctly Recalled Social Rank Cues") + scale_colour_manual(values=c("#000000", "#009E73", "#D55E00", "#0072B2",  "#F0E442","#CC79A7"))+theme(legend.position = "right")+
  expand_limits(y=c(0,8)))
```





```{r}
# Plot
d$CUE<-as.factor(d$CUE)
d <- within(d, CUE <- relevel(CUE, ref = "Prestige"))
library(ggplot2)
summary_plot<-ggplot(d, aes(GENERATION_FACTOR, RECALL, colour = CUE)) + stat_summary(fun.y = mean, geom = "line", size = 1.5, aes(group = CUE, colour = CUE)) + stat_summary(fun.y = mean, geom = "point", size = 3, aes(shape = CUE)) + stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, size = 1.60) + theme_classic(base_size = 14) + labs(x = "Experimental Transmission Chain Generation", y = "Number of Correctly Recalled Social Rank Cues") + scale_colour_manual(values=c("#000000", "#009E73", "#D55E00", "#0072B2",  "#F0E442","#CC79A7"))+theme(legend.position = c(0.9,0.9), legend.justification = c(0.9,0.9))+
  expand_limits(y=c(0,8))+scale_y_continuous(breaks = c(1,2,3,4,5,6,7,8))
summary_plot
```






```{r}
library(tidyverse)
d %>% group_by(INDIVIDUAL) %>%
summarise(mean=mean(RECALL), sd=sd(RECALL))
```



```{r}
library(tidyverse)
d %>% group_by(GENERATION_FACTOR) %>%
summarise(mean=mean(RECALL), sd=sd(RECALL))
```

```{r}
# Generation model with chain as random effect
library(brms)

mo.0<-brm(RECALL ~ mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.0, prob=0.89)
plot(mo.0)
pairs(mo.0)
```





```{r}
# INDIVIDUAL MODEL
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.1<-brm(RECALL ~ INDIVIDUAL+ mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.1, prob=0.89)
plot(mo.1)
pairs(mo.1)
marginal_effects(mo.1, probs = c(0.055, 0.945))
```


```{r}
# INDIVIDUAL MODEL (John as reference)
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JOHN'))
mo.1<-brm(RECALL ~ INDIVIDUAL+ mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.1, prob=0.89)
```


```{r}
# INDIVIDUAL MODEL WITH INTERACTION
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.2<-brm(RECALL ~ INDIVIDUAL * mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.2,prob=0.89)
plot(mo.2)
pairs(mo.2)
marginal_effects(mo.2, probs = c(0.055, 0.945))
```

```{r}
# INDIVIDUAL MODEL WITH INTERACTION (JOHN AS REFERENCE)
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JOHN'))
mo.2<-brm(RECALL ~ INDIVIDUAL * mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.2,prob=0.89)
```


```{r}
# model comparisons
(loo.0<-loo(mo.0))
(loo.1<-loo(mo.1))
(loo.2<-loo(mo.2))

#Pseudo-BMA weights
lpd_point <- cbind(
loo.0$pointwise[, "elpd_loo"],
loo.1$pointwise[, "elpd_loo"],
loo.2$pointwise[, "elpd_loo"])

# weights
library(loo)
(pbma_wts<-pseudobma_weights(lpd_point, BB=FALSE))
```



# EXPLORATORY ANALYSES (NOT INCLUDED IN PRERESGISTRATION R SCRIPT)

```{r}

# ALL EXPLORATORY VARIABLES
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.3<-brm(RECALL ~ INDIVIDUAL+ Gender + Age + mo(Football_1)+ mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.3, prob=0.89)
plot(mo.3)
pairs(mo.3)
marginal_effects(mo.3, probs = c(0.055, 0.945))
```

```{r}
# Gender
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.4<-brm(RECALL ~ INDIVIDUAL+ Gender + mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.4, prob=0.89)
plot(mo.4)
pairs(mo.4)
marginal_effects(mo.4, probs = c(0.055, 0.945))
```


```{r}
# Age
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.5<-brm(RECALL ~ INDIVIDUAL+ Age + mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.5, prob=0.89)
plot(mo.5)
pairs(mo.5)
marginal_effects(mo.5, probs = c(0.055, 0.945))
```

```{r}
# Interest in Football
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.6<-brm(RECALL ~ INDIVIDUAL+ mo(Football_1) + mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.6, prob=0.89)
plot(mo.6)
pairs(mo.6)
marginal_effects(mo.6, probs = c(0.055, 0.945))
```

```{r}
# Model comparisons
(loo.3<-loo(mo.3))
(loo.4<-loo(mo.4))
(loo.5<-loo(mo.5))
(loo.6<-loo(mo.6))
#Pseudo-BMA weights
lpd_point <- cbind(
loo.0$pointwise[, "elpd_loo"],
loo.1$pointwise[, "elpd_loo"],
loo.2$pointwise[, "elpd_loo"],
loo.3$pointwise[, "elpd_loo"],
loo.4$pointwise[, "elpd_loo"],
loo.5$pointwise[, "elpd_loo"],
loo.6$pointwise[, "elpd_loo"]
)

# weights
library(loo)
(pbma_wts<-pseudobma_weights(lpd_point, BB=FALSE))
```


# PREREGISTERED RECALL CODING SYSTEM

```{r}
# Creation of colorblind-friendly pallette
cbPalette <- c("#D55E00", "#E69F00", "#56B4E9", "#009E73", "#999999", "#CC79A7")
# Chain plots
library(ggplot2)
(chain_plot<-ggplot(d, aes(GENERATION_FACTOR, PRE_RECALL, colour = CUE)) + stat_summary(fun.y = mean, geom = "line", size = 1.3, aes(group = CUE, colour = CUE)) + stat_summary(fun.y = mean, geom = "point", size = 1, aes(shape = CUE)) + theme_classic() + facet_wrap(~ CHAIN) + labs(x = "Experimental Transmission Chain Generation", y = "Number of Correctly Recalled Social Rank Cues") + scale_colour_manual(values=c("#000000", "#009E73", "#D55E00", "#0072B2",  "#F0E442","#CC79A7"))+theme(legend.position = "right")+
  expand_limits(y=c(0,8)))
```






```{r}
(summaryplot<-ggplot(d, aes(GENERATION_FACTOR, PRE_RECALL, colour = CUE)) + stat_summary(fun.y = mean, geom = "line", size = 1.5, aes(group = CUE, colour = CUE)) + stat_summary(fun.y = mean, geom = "point", size = 3, aes(shape = CUE)) + stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, size = 1.60) + theme_classic(base_size = 16) + labs(x = "Experimental Transmission Chain Generation", y = "Number of Correctly Recalled Social Rank Cues") + scale_colour_manual(values=c("#000000", "#009E73", "#D55E00", "#0072B2",  "#F0E442","#CC79A7"))+theme(legend.position = c(0.9,0.9), legend.justification = c(0.9,0.9))+
  expand_limits(y=c(0,8))+scale_y_continuous(breaks = c(1,2,3,4,5,6,7,8)))
```

```{r}
library(tidyverse)
d %>% group_by(INDIVIDUAL) %>%
summarise(mean=mean(RECALL), sd=sd(RECALL))
```



```{r}
library(tidyverse)
d %>% group_by(GENERATION_FACTOR) %>%
summarise(mean=mean(RECALL), sd=sd(RECALL))
```

```{r}
# Generation model with chain as random effect
library(brms)

mo.0<-brm(PRE_RECALL ~ mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.0, prob=0.89)
plot(mo.0)
pairs(mo.0)
```





```{r}
# INDIVIDUAL MODEL
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.1<-brm(PRE_RECALL ~ INDIVIDUAL+ mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.1, prob=0.89)
plot(mo.1)
pairs(mo.1)
marginal_effects(mo.1, probs = c(0.055, 0.945))
```


```{r}
# INDIVIDUAL MODEL (John as reference)
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JOHN'))
mo.1<-brm(PRE_RECALL ~ INDIVIDUAL+ mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.1, prob=0.89)
```


```{r}
# INDIVIDUAL MODEL WITH INTERACTION
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.2<-brm(PRE_RECALL ~ INDIVIDUAL * mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.2,prob=0.89)
plot(mo.2)
pairs(mo.2)
marginal_effects(mo.2, probs = c(0.055, 0.945))
```

```{r}
# INDIVIDUAL MODEL WITH INTERACTION (JOHN AS REFERENCE)
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JOHN'))
mo.2<-brm(PRE_RECALL ~ INDIVIDUAL * mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.2,prob=0.89)
```


```{r}
# model comparisons
(loo.0<-loo(mo.0))
(loo.1<-loo(mo.1))
(loo.2<-loo(mo.2))

#Pseudo-BMA weights
lpd_point <- cbind(
loo.0$pointwise[, "elpd_loo"],
loo.1$pointwise[, "elpd_loo"],
loo.2$pointwise[, "elpd_loo"])

# weights
library(loo)
(pbma_wts<-pseudobma_weights(lpd_point, BB=FALSE))
```



# EXPLORATORY ANALYSES (NOT INCLUDED IN PREREGISTRATION)

```{r}

# ALL EXPLORATORY VARIABLES
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.3<-brm(PRE_RECALL ~ INDIVIDUAL+ Gender + Age + mo(Football_1)+ mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.3, prob=0.89)
plot(mo.3)
pairs(mo.3)
marginal_effects(mo.3, probs = c(0.055, 0.945))
```

```{r}
# Gender
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.4<-brm(PRE_RECALL ~ INDIVIDUAL+ Gender + mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.4, prob=0.89)
plot(mo.4)
pairs(mo.4)
marginal_effects(mo.4, probs = c(0.055, 0.945))
```


```{r}
# Age
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.5<-brm(PRE_RECALL ~ INDIVIDUAL+ Age + mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.5, prob=0.89)
plot(mo.5)
pairs(mo.5)
marginal_effects(mo.5, probs = c(0.055, 0.945))
```

```{r}
# Interest in Football
d <- within(d, INDIVIDUAL <- relevel(INDIVIDUAL, ref = 'JAMES'))
mo.6<-brm(PRE_RECALL ~ INDIVIDUAL+ mo(Football_1) + mo(GENERATION_NUMERIC) + (1|CHAIN), data = d, family = "poisson")
summary(mo.6, prob=0.89)
plot(mo.6)
pairs(mo.6)
marginal_effects(mo.6, probs = c(0.055, 0.945))
```

```{r}
# Model comparisons
(loo.3<-loo(mo.3))
(loo.4<-loo(mo.4))
(loo.5<-loo(mo.5))
(loo.6<-loo(mo.6))
#Pseudo-BMA weights
lpd_point <- cbind(
loo.0$pointwise[, "elpd_loo"],
loo.1$pointwise[, "elpd_loo"],
loo.2$pointwise[, "elpd_loo"],
loo.3$pointwise[, "elpd_loo"],
loo.4$pointwise[, "elpd_loo"],
loo.5$pointwise[, "elpd_loo"],
loo.6$pointwise[, "elpd_loo"]
)

# weights
library(loo)
(pbma_wts<-pseudobma_weights(lpd_point, BB=FALSE))
```


